Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-08 chapters/paper1_5.tex
Changes 1. Updatd methods section 2. Changed scale of some plots 3. Updated references with new ones

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/particle_layer.png}%
\caption{Visualizations of the order parameter $\phi$ for bijels stabilized by oblate (left), spherical (middle) and prolate (right) particles 
         after $10^5$ simulation time steps. The top row shows the structure of bijels formed in the 
         absence of a magnetic field, while the bottom row shows the structure of bijels formed at $\bar{B} = 1$. 
         The direction of the magnetic field is indicated by the arrow.
\label{fig:particle_layer}}%
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/steinhardt_time.png}%
\caption{Time dependence of the Steinhardt order parameters $q_2$ and $q_4$ for different particles shapes $\alpha$ and at different magnetic field strengths $\bar{B}$. The filled bands around the lines indicate the standard deviation over three independent simulation runs.}
\label{fig:steinhardt_time}%
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/steinhardt_field.png}%
\caption{Dependence of the Steinhardt order parameter $q_2$ and $q_4$ on the magnetic field $\bar{B}$. The order parameters were computed for the final 
         bijel microstructure after $10^5$ simulation time steps. Errorbars indicate the standard deviation taken over three independent simulation runs.
\label{fig:steinhardt_field}}%
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/curvature_field.png}%
\caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian $\langle K \rangle \Sigma^{-2}$ curvature in the left and right 
         respectively. Each plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ at the final timestep averaged across 
         3 runs for particles with $\alpha = 0.5, 1, 2$. We observe that the mean curvature does not demonstrate any trends, while the Gaussian curvature 
         shows a reduction as the magnetic field strength is increased for ellipsoidal particles.}
\label{fig:curvature_field}%
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/handles_time.png}%
\caption{Time dependence of the number of channels for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$. 
         The bands around the lines indicate the standard deviation taken over three independent simulation results. The number of channels roughly 
         follows a power law behavior $\sim t^{-3/2}$ which suggests that it is inversely proportional to the characteristic domain size $L \sim t^{3/2}$.
\label{fig:handles_time}}%
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/CSD.png}%
\caption{Channel size distribution (CSD) in bijels stabilized by oblate ($\alpha=0.5$), spherical ($\alpha=1.0$), and prolate ($\alpha=2.0$) particles. 
         The channel size distribution was obtained as the negative derivative of the number of handles in isodistance structures of the Euclidean distance 
         transform of the order parameter field. The negative values are due to numerical artifacts when calculating the number of handles as a function of 
         isodistance from the interface.}
\label{fig:CSD}%
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{../figures/results/paper1_5/channel_size_field.png}%
\caption{Average channel size $L_c$ for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$. The average channel size was calculated from the channel size distribution shown in Fig.~\ref{fig:CSD}. Errorbars indicate the standard deviation taken over three independent simulation runs.
\label{fig:channel_size_field}}%
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale = 0.4]{../figures/results/paper1_5/particle_layer.png}%
\caption{Visualizations of the order parameter $\phi$ for bijels stabilized by oblate (left), spherical (middle) and prolate (right) particles 
         after $10^5$ simulation time steps. The top row shows the structure of bijels formed in the 
         absence of a magnetic field, while the bottom row shows the structure of bijels formed at $\bar{B} = 1$. 
         The direction of the magnetic field is indicated by the arrow.
\label{fig:particle_layer}}%
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale = 0.38]{../figures/results/paper1_5/steinhardt_time.png}%
\caption{Time dependence of the Steinhardt order parameters $q_2$ and $q_4$ for different particles shapes $\alpha$ and at different magnetic field strengths $\bar{B}$. The filled bands around the lines indicate the standard deviation over three independent simulation runs.}
\label{fig:steinhardt_time}%
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.45]{../figures/results/paper1_5/steinhardt_field.png}%
\caption{Dependence of the Steinhardt order parameter $q_2$ and $q_4$ on the magnetic field $\bar{B}$. The order parameters were computed for the final 
         bijel microstructure after $10^5$ simulation time steps. Errorbars indicate the standard deviation taken over three independent simulation runs.
\label{fig:steinhardt_field}}%
\end{figure}

@@

\begin{figure}
    \centering
\includegraphics[scale=0.5]{../figures/results/paper1_5/curvature_field.png}%
\caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian $\langle K \rangle \Sigma^{-2}$ curvature in the left and right 
         respectively. Each plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ at the final timestep averaged across 
         3 runs for particles with $\alpha = 0.5, 1, 2$. We observe that the mean curvature does not demonstrate any trends, while the Gaussian curvature 
         shows a reduction as the magnetic field strength is increased for ellipsoidal particles.}
\label{fig:curvature_field}%
\end{figure}

@@

\begin{figure}
    \centering
\includegraphics[scale=0.45]{../figures/results/paper1_5/handles_time.png}%
\caption{Time dependence of the number of channels for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$. 
         The bands around the lines indicate the standard deviation taken over three independent simulation results. The number of channels roughly 
         follows a power law behavior $\sim t^{-3/2}$ which suggests that it is inversely proportional to the characteristic domain size $L \sim t^{3/2}$.
\label{fig:handles_time}}%
\end{figure}

@@

\begin{figure}
    \centering
\includegraphics[scale = 0.4]{../figures/results/paper1_5/CSD.png}%
\caption{Channel size distribution (CSD) in bijels stabilized by oblate ($\alpha=0.5$), spherical ($\alpha=1.0$), and prolate ($\alpha=2.0$) particles. 
         The channel size distribution was obtained as the negative derivative of the number of handles in isodistance structures of the Euclidean distance 
         transform of the order parameter field. The negative values are due to numerical artifacts when calculating the number of handles as a function of 
         isodistance from the interface.}
\label{fig:CSD}%
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale = 0.6]{../figures/results/paper1_5/channel_size_field.png}%
\caption{Average channel size $L_c$ for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$. The average channel size was calculated from the channel size distribution shown in Fig.~\ref{fig:CSD}. Errorbars indicate the standard deviation taken over three independent simulation runs.
\label{fig:channel_size_field}}%
\end{figure}

### 2025-04-08 chapters/paper1_new.tex
Changes 1. Updatd methods section 2. Changed scale of some plots 3. Updated references with new ones

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../figures/results/paper1/microstructure_viz.png}
    \caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right). 
             The top row shows the structure forming without a magnetic field. The bottom row shows the structure forming in an applied magnetic 
             field of reduced strength $\bar{B}=1.0$. The snapshots are colored according to the order parameter $\phi$.}
    \label{fig:microstructure_viz}
\end{figure}

@@

    \begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../figures/results/paper1/particle_packing_viz.png}
    \caption{Snapshots illustrating the particle packing at the interface for different particle shapes $\alpha$ with (left)
     and without (right) applied magnetic field $\bar{B}$. The right column shows the alignment of the symmetry axis of the oblate (top row) and prolate (bottom row) 
     particles in the direction of the magnetic field indicated by arrows.}
    \label{fig:packing_viz}
    \end{figure}

@@

    \begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../figures/results/paper1/S-vs-t.png}
    \caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different field strength $\bar{B}$. Errorbars indicate the standard deviation taken over three independent simulation runs. Nematic order generally increases with applied field strength for all particle geometries. The increase slows down (for prolate particles) or reverses (for oblate particles) around $10^4$ timesteps.}
    \label{fig:nematic_time}
    \end{figure}

@@

    \begin{figure}
    \includegraphics[width=\columnwidth]{../figures/results/paper1/interface_nematic.png}
    \caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. The interface alignment tends to increase with increasing field strength. The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
    \label{fig:interface_nematic}
    \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../figures/results/paper1/psi-vs-t.png}
    \caption{Time-dependence of the average angle $\psi$ between the particle axis and the interface normal for oblate ($\alpha=0.5$) and 
             prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. Errorbars indicate the standard deviation taken over 
             three independent simulation runs. The angle between between the particles and the interface normal generally approaches the energetically 
             preferred value ($0^\circ$ for oblate particls, $90^\circ$ for prolate particles). The average angle changes most rapidly around $10^4$ timesteps.}
\label{fig:psi_time}
\end{figure}

@@

    \begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/paper1/rdf_compare_time.png}
    \caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic field strength $\bar{B}$. The radial 
    distribution function is shown at $10^3$, $10^4$, and $10^5$ timesteps. The distance $r$ is normalized by the radius $R=\max(R_\parallel,R_\perp)$ 
    of the larger particle axis. The peaks illustrate the packing of particles in the interface. Dashed lines indicate the side-by-side, tip-to-tip, and 
    side-to-tip configuration of particle pairs. For spherical particles, the three values are identical.}
    \label{fig:rdf}
    \end{figure*}

>>>>

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{../figures/results/paper1/microstructure_viz.png}
    \caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right). 
             The top row shows the structure forming without a magnetic field. The bottom row shows the structure forming in an applied magnetic 
             field of reduced strength $\bar{B}=1.0$. The snapshots are colored according to the order parameter $\phi$.}
    \label{fig:microstructure_viz}
\end{figure}

@@

    \begin{figure}
    \centering
    \includegraphics[scale=0.6]{../figures/results/paper1/particle_packing_viz.png}
    \caption{Snapshots illustrating the particle packing at the interface for different particle shapes $\alpha$ with (left)
     and without (right) applied magnetic field $\bar{B}$. The right column shows the alignment of the symmetry axis of the oblate (top row) and prolate (bottom row) 
     particles in the direction of the magnetic field indicated by arrows.}
    \label{fig:packing_viz}
    \end{figure}

@@

    \begin{figure}
    \centering
    \includegraphics[scale=0.6]{../figures/results/paper1/S-vs-t.png}
    \caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different field strength $\bar{B}$. Errorbars indicate the standard deviation taken over three independent simulation runs. Nematic order generally increases with applied field strength for all particle geometries. The increase slows down (for prolate particles) or reverses (for oblate particles) around $10^4$ timesteps.}
    \label{fig:nematic_time}
    \end{figure}

@@

    \begin{figure}
        \centering
    \includegraphics[scale=0.6]{../figures/results/paper1/interface_nematic.png}
    \caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. The interface alignment tends to increase with increasing field strength. The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
    \label{fig:interface_nematic}
    \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{../figures/results/paper1/psi-vs-t.png}
    \caption{Time-dependence of the average angle $\psi$ between the particle axis and the interface normal for oblate ($\alpha=0.5$) and 
             prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. Errorbars indicate the standard deviation taken over 
             three independent simulation runs. The angle between between the particles and the interface normal generally approaches the energetically 
             preferred value ($0^\circ$ for oblate particls, $90^\circ$ for prolate particles). The average angle changes most rapidly around $10^4$ timesteps.}
\label{fig:psi_time}
\end{figure}

@@

    \begin{figure*}
    \centering
    \includegraphics[scale=0.4]{../figures/results/paper1/rdf_compare_time.png}
    \caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic field strength $\bar{B}$. The radial 
    distribution function is shown at $10^3$, $10^4$, and $10^5$ timesteps. The distance $r$ is normalized by the radius $R=\max(R_\parallel,R_\perp)$ 
    of the larger particle axis. The peaks illustrate the packing of particles in the interface. Dashed lines indicate the side-by-side, tip-to-tip, and 
    side-to-tip configuration of particle pairs. For spherical particles, the three values are identical.}
    \label{fig:rdf}
    \end{figure*}

### 2025-04-08 chapters/paper2.tex
Changes 1. Updatd methods section 2. Changed scale of some plots 3. Updated references with new ones

\begin{figure} 
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/microstructure_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The top 
         row detail the microstructure evolution for bijels with no applied field while the bottom rows show bijels stabilized by oblate and prolate particles 
         respectively with a field strength of $\bar{B} = 1$ applied.}
\label{fig:microstructure_viz-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/particle_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial and final timesteps, 
         both in the absence of a magnetic field (top row) and with a magnetic field applied (\(\bar{B}_z = 1\), bottom row). Particle reorientation to the
         applied field can be observed.} 
\label{fig:particle_viz-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/domain_size_aniso-field_on.png} 
    \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels 
             stabilized with magnetically responsive oblate and prolate ellipsoids. We see that upon application of the field, bijels stabilized with prolate 
             particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size 
             perpendicular to the applied field, $L_{\perp}$ decreases. The opposite is true for bijels stabilized with oblate particles. The tortuosity data 
             demonstrate that as the domain size increases, the tortuosity decreases and vice versa.} 
    \label{fig:domain_size_aniso-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_up.png} 
\caption{Snapshots of the structural evolution of the particle monolayer in bijels stabilized by prolate ellipsoids 
         under different magnetic field conditions. The top row corresponds to a simulation where the field is increased from 
         \(\bar{B} = 0.2\) to \(\bar{B} = 1.0\), while the bottom row shows a system maintained at a constant field of \(\bar{B} = 1.0\) throughout.} 
\label{fig:particle_viz-field_up} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_down.png} 
\caption{Snapshots of bijels stabilized by prolate ellipsoids at 
         the initial and final time steps after the removal of an applied magnetic field. The top row corresponds to the case where 
         the field is reduced from \(\bar{B} = 0.2 \rightarrow 0.0\), and the bottom row from \(\bar{B} = 1.0 \rightarrow 0.0\)}
\label{fig:microstructure_viz-field_down}
\end{figure}

>>>>

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/microstructure_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The top 
         row detail the microstructure evolution for bijels with no applied field while the bottom rows show bijels stabilized by oblate and prolate particles 
         respectively with a field strength of $\bar{B} = 1$ applied.}
\label{fig:microstructure_viz-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial and final timesteps, 
         both in the absence of a magnetic field (top row) and with a magnetic field applied (\(\bar{B}_z = 1\), bottom row). Particle reorientation to the
         applied field can be observed.} 
\label{fig:particle_viz-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/domain_size_aniso-field_on.png} 
    \caption{Plots of the anisotropic domain size (left) and tortuosity (right) as a function of magnetic field strength for bijels 
             stabilized with oblate and prolate ellipsoids when raising the applied magnetic field. Prolate-stabilized bijels 
             exhibit increased domain size parallel to the field ($L_{\parallel}$) and decreased size perpendicular ($L_{\perp}$), 
             while the opposite trend is observed for oblate-stabilized systems. Tortuosity inversely correlates with domain size in 
             both cases.} 
    \label{fig:domain_size_aniso-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/particle_viz-field_up.png} 
\caption{Snapshots of the structural evolution of the particle monolayer in bijels stabilized by prolate ellipsoids 
         under different magnetic field conditions. The top row corresponds to a simulation where the field is increased from 
         \(\bar{B} = 0.2\) to \(\bar{B} = 1.0\), while the bottom row shows a system maintained at a constant field of \(\bar{B} = 1.0\) throughout.} 
\label{fig:particle_viz-field_up} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.45]{../figures/results/paper2/microstructure_viz-field_down.png} 
\caption{Snapshots of bijels stabilized by prolate ellipsoids at 
         the initial and final time steps after the removal of an applied magnetic field. The top row corresponds to the case where 
         the field is reduced from \(\bar{B} = 0.2 \rightarrow 0.0\), and the bottom row from \(\bar{B} = 1.0 \rightarrow 0.0\)}
\label{fig:microstructure_viz-field_down}
\end{figure}
